---
title: "Which way should I present my results"
output: 
  html_document:
    toc: yes
    toc_float: yes
date: "2022-11-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.asp = 1, fig.pos = "center")
pacman::p_load(tidyverse, phdWork)
```

```{r}
set.seed(1234)
s <- sample(1:nrow(cobre), 10)
df_train <- cobre %>%
  select(cors, age, group) %>% 
  slice(-s)
df_test <- cobre %>%
  select(cors, age, group) %>% 
  slice(s)

model_formula <- ~ age + group
X_train <- df_train$cors
X_test <- df_test$cors
Y_train <- model.matrix(model_formula, data = df_train) %>%
  as.matrix() %>%
  .[, -1]
Y_test <- model.matrix(model_formula, data = df_test) %>%
  as.matrix() %>%
  .[, -1]
```

```{r}
M <- riemannian_pls(X = X_train, Y = Y_train, L = 3, tol = 1e-4, max.iter = 20,
                    type_x = "affine", type_y = "euclidean", method = "tangent",
                    scale = TRUE, mc.cores = 6)
```

```{r}
preds <- predict.riemannian_pls(object = M, newdata = X_test, tol = 1e-4, max.iter = 20,
                                method = "tangent")
y <- t((t(Y_test) - M$muY)/M$Y_sd)
```

```{r}
preds %>% 
  as_tibble() %>% 
  select(pred = contains("group")) %>% 
  mutate(pred = ifelse(pred < 0, levels(df_test$group)[1], levels(df_test$group)[2]),
         pred = factor(pred, levels(df_test$group))) %>% 
  add_column(truth = df_test$group) %>% 
  met_set(truth = truth, estimate = pred) %>% 
  select(-.estimator) %>% 
  pivot_wider(names_from = .metric, values_from = .estimate)
```

```{r}
get_model_metrics(M = M, test_data = df_test, L = 2, formula = ~age + group)
```



```{r}
cancor(preds, y)
```

```{r}
tibble(
  truth = y[, 2],
  est = preds[, 2]
) %>% 
yardstick::rsq(truth = truth, estimate = est)
```

```{r}
tibble(
  truth = y[, 2],
  est = preds[, 2]
) %>% 
yardstick::rsq_trad(truth = truth, estimate = est)
```




```{r}
rsq.riemannian_pls(truth = y, est = preds, m = M$muY, type_y = "euclidean", 
                   test = FALSE)
rsq.riemannian_pls(truth = y, est = preds, m = M$muY, type_y = "euclidean", 
                   test = TRUE)
rmse.riemannian_pls(truth = y, est = preds, m = M$muY, type_y = "euclidean")
```

```{r}
tmp <- fitted.riemannian_pls(M)
```

```{r}
sqrt(sum((scale(Y_train) - tmp)^2)/nrow(tmp))
```

```{r}
1 - sum((scale(Y_train) - tmp)^2)/sum(scale(Y_train)^2)
```

```{r}
sum((t(tmp))^2)/sum(scale(Y_train)^2)
```






I have fit the Riemannian PLS model to the COBRE data using the tangent space approximation.  My response was the variables age and group, centered and scaled.  My predictors where my FC matrices.

## Cross validation results

```{r}
cv_res <- read_rds("../results/cobre_cv_results.Rds")
```

```{r}
cv_res %>% 
  filter(K < 50) %>%
  pivot_longer(-(id:K), names_to = "metric") %>% 
  group_by(K, metric) %>% 
  summarise(m = mean(value), s = sd(value), .groups = "drop") %>% 
  ggplot(aes(x = K, y = m, colour = metric)) +
  geom_linerange(aes(ymin = m - s, ymax = m + s)) +
  geom_point() +
  facet_wrap(~metric, ncol = 1, scales = "free_y") +
  harrypotter::scale_color_hp_d("ravenclaw") +
  theme_classic()
```

> Results

- Best achieved at K = 3, within 1 sd can take K = 1
- K = 1 is boring, so I consider K = 3

```{r, eval = FALSE}
M <- riemannian_pls(X = X, Y = Y, L = 3, tol = 1e-4, max.iter = 20,
                    type_x = "affine", type_y = "euclidean", method = "tangent",
                    scale = TRUE)
write_rds(M, "../results/cobre_model.Rds")
```

```{r}
M <- read_rds("../results/cobre_model.Rds")
```

## Using the loadings

I can present my results using the loadings directly:




```{r}
get_loading_plot <- function(L){
  C <- unvec(P = M$muX, vec = M$loadingsX[[L]])
  y_lod <- M$loadingsY[[L]]
  
  dat <- C %>% 
    as_tibble(rownames = "source") %>% 
    mutate(source = fct_inorder(source),
           source = fct_rev(source)) %>% 
    pivot_longer(-source, names_to = "target") %>% 
    mutate(target = factor(target, levels = levels(source)),
           target = fct_rev(target),
           value = ifelse(abs(value) < quantile(abs(value), 0.9), 0, value))
  
  
  p <- dat %>% 
    ggplot(aes(x = target, y = source, colour = value)) +
    geom_point(size = 2) +
    scale_x_discrete(position = "top") +
    scale_colour_distiller(palette = "RdBu", direction = 1)+
    labs(x = NULL, y = NULL, colour = NULL) +
    ggtitle(str_c("Y loadings\n age = ", round(y_lod[1,1], 3),
                  " | group = ", round(y_lod[2,1], 3))) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90),
          plot.title = element_text(hjust = 0.5))
  return(p)
}
```

### Plots {.tabset}

#### Loading 1

```{r}
L1 <- get_loading_plot(1)
L1
```


#### Loading 2

```{r}
L2 <- get_loading_plot(2)
L2
```


#### Loading 3

```{r}
L3 <- get_loading_plot(3)
L3
```


## Using the regression coefficients

Alternatively, since I have it this model using the tangent space approximation, I have really just done Euclidean PLS on transformed data.  Hence, I can consider the prediction equation for Euclidean PLS that gives

\[
\hat{Y} = X \beta_{pls}
\]

where

\[
\beta_{pls} = W (P^TW)^{-1} B C^T\, .
\]

Then $\beta_{pls}$ is a matrix whose columns represent the response variables (age and group) and whose rows represent different FC connections.  I can visualise these as follows:

```{r}
P.hat <- do.call(cbind, M$loadingsX)
W.hat <- do.call(cbind, M$weightsX)
C.hat <- do.call(cbind, M$weightsY)
B.hat <- map_dbl(M$reg_steps, ~.x$b1) %>% 
  diag()
B <- W.hat %*% solve(t(P.hat) %*% W.hat) %*% B.hat %*% t(C.hat)
```

```{r}
get_coeff_plot <- function(name){
  if(name == "age"){
    C <- unvec(P = M$muX, vec = B[, 1])
  }else{
    C <- unvec(P = M$muX, vec = B[, 2])
  }
  dat <- C %>% 
    as_tibble(rownames = "source") %>% 
    mutate(source = fct_inorder(source),
           source = fct_rev(source)) %>% 
    pivot_longer(-source, names_to = "target") %>% 
    mutate(target = factor(target, levels = levels(source)),
           target = fct_rev(target),
           value = ifelse(abs(value) < quantile(abs(value), 0.9), 0, value))
  
  p <- dat %>% 
    ggplot(aes(x = target, y = source, colour = value)) +
    geom_point(size = 2) +
    scale_x_discrete(position = "top") +
    scale_colour_distiller(palette = "RdBu", direction = 1)+
    labs(x = NULL, y = NULL, colour = NULL) +
    ggtitle(str_c(name)) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 90),
          plot.title = element_text(hjust = 0.5))
  
  return(p)
}
```

### Plots {.tabset}

#### Age coefficients

```{r}
A <- get_coeff_plot("age")
A
```



#### Group coefficients

```{r}
G <- get_coeff_plot("group")
G
```


```{r}
levels(cobre$group)
```

```{r}
unique(abide_aal$group)
```

