---
title: "Exploratory plots"
output: 
  html_document:
    toc: yes
    toc_float: yes
date: "2022-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.asp = 1.5)
pacman::p_load(tidyverse, patchwork)
```



```{r}
get_data <- function(folder){
  fl <- list.files(here::here(glue::glue("results/{folder}")), full.names = T, recursive = T)
  fl <- fl[!str_detect(fl, "presim")]
  
  df <- map_dfr(fl, read_rds)
  return(df)
}

make_plots <- function(df, var, x_type, y_type){
  df <- df %>% 
    filter(type_x == x_type, type_y == y_type) %>% 
    rename(var = all_of(var)) %>% 
    mutate(K = as.factor(K), var = as.factor(var))
  
  
  p1 <- df %>% 
    select(K, var, P_r2, Q_r2) %>% 
    pivot_longer(-c(K, var)) %>% 
    ggplot(aes(x = K, y = value, fill = var)) +
    geom_boxplot(show.legend = FALSE) +
    facet_wrap(~name, ncol = 2) +
    theme_classic()
  p2 <- df %>% 
    select(K, var, X_r2, Y_r2) %>% 
    pivot_longer(-c(K, var)) %>% 
    ggplot(aes(x = K, y = value, fill = var)) +
    geom_boxplot(show.legend = FALSE) +
    facet_wrap(~name, ncol = 2) +
    theme_classic()
  p3 <- df %>% 
    select(K, var, X_rmse, Y_rmse) %>% 
    pivot_longer(-c(K, var)) %>% 
    ggplot(aes(x = K, y = value, fill = var)) +
    geom_boxplot() +
    facet_wrap(~name, ncol = 2) +
    theme_classic() +
    labs(fill = var) +
    theme(legend.position = "bottom")
  
  return(p1/p2/p3)
}

```

## Noise

```{r}
var_folder_name <- "noise"
var <- "sig"
df <- get_data(var_folder_name)
```


### Number of sims completed

```{r, fig.asp = 1}
df %>% 
  count(type_x, type_y, K, sig) %>% 
  mutate(K = as.factor(K), sig = as.factor(sig),
         flag = case_when(
           n < 100 ~ "1. Too little sims",
           n == 100 ~ "2. Just Right",
           TRUE ~ "3. Too many sims"
         )) %>% 
  ggplot(aes(x = K, y = sig, label = n, fill = flag)) +
  geom_label() +
  facet_grid(type_y ~ type_x) +
  theme_classic() +
  theme(legend.position = "bottom")
```

### Plots {.tabset}
#### Affine vs Affine

```{r}
make_plots(df, var, "affine", "affine")
```


#### Affine vs Euclidean

```{r}
make_plots(df, var, "affine", "euclidean")
```


#### Euclidean vs affine

```{r}
make_plots(df, var, "euclidean", "affine")
```





## Sample Size

```{r}
var_folder_name <- "sample_size"
var <- "n"
df <- get_data(var_folder_name)
```


### Number of sims completed

```{r, fig.asp = 1}
df %>% 
  count(type_x, type_y, K, n, name = "nn") %>% 
  mutate(K = as.factor(K), n = as.factor(n),
         flag = case_when(
           nn < 100 ~ "1. Too little sims",
           nn == 100 ~ "2. Just Right",
           TRUE ~ "3. Too many sims"
         )) %>% 
  ggplot(aes(x = K, y = n, label = nn, fill = flag)) +
  geom_label() +
  facet_grid(type_y ~ type_x) +
  theme_classic() +
  theme(legend.position = "bottom")
```

### Plots {.tabset}

#### Affine vs Affine

```{r}
make_plots(df, var, "affine", "affine")
```

#### Affine vs Euclidean

```{r}
make_plots(df, var, "affine", "euclidean")
```


#### Euclidean vs affine

```{r}
make_plots(df, var, "euclidean", "affine")
```





## q

```{r}
var_folder_name <- "q"
var <- "y_dim"
df <- get_data(var_folder_name)
```


### Number of sims completed

```{r, fig.asp = 1}
df %>% 
  count(type_x, type_y, K, y_dim) %>% 
  mutate(K = as.factor(K), y_dim = as.factor(y_dim),
         flag = case_when(
           n < 100 ~ "1. Too little sims",
           n == 100 ~ "2. Just Right",
           TRUE ~ "3. Too many sims"
         )) %>% 
  ggplot(aes(x = K, y = y_dim, label = n, fill = flag)) +
  geom_label() +
  facet_grid(type_y ~ type_x) +
  theme_classic() +
  theme(legend.position = "bottom")
```


### Plots {.tabset}

#### Affine vs Affine

```{r}
make_plots(df, var, "affine", "affine")
```

#### Affine vs Euclidean

```{r}
make_plots(df, var, "affine", "euclidean")
```


#### Euclidean vs affine

```{r}
make_plots(df, var, "euclidean", "affine")
```





## p

```{r}
var_folder_name <- "p"
var <- "x_dim"
df <- get_data(var_folder_name)
```


### Number of sims completed

```{r, fig.asp = 1}
df %>% 
  count(type_x, type_y, K, x_dim) %>% 
  mutate(K = as.factor(K), x_dim = as.factor(x_dim),
         flag = case_when(
           n < 100 ~ "1. Too little sims",
           n == 100 ~ "2. Just Right",
           TRUE ~ "3. Too many sims"
         )) %>% 
  ggplot(aes(x = K, y = x_dim, label = n, fill = flag)) +
  geom_label() +
  facet_grid(type_y ~ type_x) +
  theme_classic() +
  theme(legend.position = "bottom")
```

### Plots {.tabset}

#### Affine vs Affine

```{r}
make_plots(df, var, "affine", "affine")
```

#### Affine vs Euclidean

```{r}
make_plots(df, var, "affine", "euclidean")
```


#### Euclidean vs affine

```{r}
make_plots(df, var, "euclidean", "affine")
```





## sub

```{r}
var_folder_name <- "sub"
var <- "x_dim"
df <- get_data(var_folder_name)
```


### Number of sims completed

```{r, fig.asp = 1}
df %>% 
  count(type_x, type_y, K, x_dim) %>% 
  mutate(K = as.factor(K), x_dim = as.factor(x_dim),
         flag = case_when(
           n < 10 ~ "1. Too little sims",
           n == 10 ~ "2. Just Right",
           TRUE ~ "3. Too many sims"
         )) %>% 
  ggplot(aes(x = K, y = x_dim, label = n, fill = flag)) +
  geom_label() +
  facet_grid(type_y ~ type_x) +
  theme_classic() +
  theme(legend.position = "bottom")
```

### Plots {.tabset}

#### Affine vs Affine

```{r}
make_plots(df, var, "affine", "affine")
```
```{r}
df %>% 
    filter(type_x == "affine", type_y == "affine") %>% 
    rename(var = all_of("x_dim")) %>% 
    mutate(K = as.factor(K), 
           var = as.factor(var),
           sig = as.factor(sig)) %>% 
  select(K, var, sig, P_r2, Q_r2) %>% 
    pivot_longer(-c(K, var, sig)) %>% 
    ggplot(aes(x = K, y = value, fill = sig)) +
    geom_boxplot(show.legend = T) +
    facet_grid(var~name) +
    theme_classic()
```

```{r}
  
  p1 <- df %>% 
    select(K, var, P_r2, Q_r2) %>% 
    pivot_longer(-c(K, var)) %>% 
    ggplot(aes(x = K, y = value, fill = var)) +
    geom_boxplot(show.legend = FALSE) +
    facet_wrap(~name, ncol = 2) +
    theme_classic()
  p2 <- df %>% 
    select(K, var, X_r2, Y_r2) %>% 
    pivot_longer(-c(K, var)) %>% 
    ggplot(aes(x = K, y = value, fill = var)) +
    geom_boxplot(show.legend = FALSE) +
    facet_wrap(~name, ncol = 2) +
    theme_classic()
  p3 <- df %>% 
    select(K, var, X_rmse, Y_rmse) %>% 
    pivot_longer(-c(K, var)) %>% 
    ggplot(aes(x = K, y = value, fill = var)) +
    geom_boxplot() +
    facet_wrap(~name, ncol = 2) +
    theme_classic() +
    labs(fill = var) +
    theme(legend.position = "bottom")
```

